IMPC Mouse data - Variance in sex differences

### 2019-11-20 scripts/2019_Nov1-FiguresRearranged_IMPC_variance_and_sex_difference.Rmd
Ensure grouping variable is removed.
In tidyr 0.8.3, nest removes the group variable. But in tydr 1.0.0 the bahviour changes. Adding ungroup should ensure some consistency

```{r}
library(readr)
library(dplyr)
library(metafor)
library(devtools)
library(purrr)
library(tidyverse)
library(tibble)
library(kableExtra)
library(robumeta)
library(ggpubr)
library(ggplot2)
```

@@

```{r}
# nesting
n_count <- meta1_sub %>% 
  group_by(parameter_group) %>% 
  mutate(raw_N = sum(sampleSize)) %>%  
    nest()

@@

robu_all <- full_join(robusub_CVR, robusub_VR) %>% full_join(., robusub_RR)
kable(cbind(robu_all, robu_all)) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

>>>>

```{r}
library(readr)
library(dplyr)
library(metafor)
library(devtools)
library(purrr)
library(tidyverse)
library(tibble)
library(kableExtra)
library(robumeta)
library(ggpubr)
library(ggplot2)

@@

```{r}
# nesting
n_count <- meta1_sub %>% 
  group_by(parameter_group) %>% 
  mutate(raw_N = sum(sampleSize)) %>%  
  nest() %>% 
  ungroup()

@@

robu_all <- full_join(robusub_CVR, robusub_VR) %>% full_join(., robusub_RR)
```

```{r}
kable(cbind(robu_all, robu_all)) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")
```
